My title

### 2023-03-30 outputs/paper/paper.qmd
Graphing respondents' degree

clean_data_respondent |>
  ggplot(aes(x = degrees_clean)) +
  geom_bar(fill = "slateblue1") +
  theme_minimal() +
  labs(x = "Highest Education Level",
       y = "Number of Participants",
       title = "Education Level of the Respondant.")

>>>>

clean_data_degree |>
  ggplot(aes(x = degree)) +
  geom_bar(fill = "slateblue1") +
  theme_minimal() +
  labs(x = "Degree Obtained",
       y = "Number of Participants",
       title = "Degree obtained by participant")
```
